---
title: "Data Science Intro"
format: html
editor: visual
---

## Questions About Data Scientists

### What do you think being a data scientist is about?

I think that being a data scientist can mean several things. Chapter 1 of the *Practitioner's Guide to Data Science* broke this question down very well in my opinion. I think being a data scientist can mean one or more of the following:

-   Engineering
    -   Sometimes a data scientist might focus on the processes and functions that make working with data possible.
-   Analysis
    -   Other data scientists will focus on turning the raw data into useful information for another audience through exploratory analysis.
-   Modeling
    -   Finally, some data scientists focus on modeling data to make future predictions or find patterns in the data that are not immediately apparent.

### What differences/similarities do you see between data scientists and statisticians?

The biggest difference between a data scientist and a statistician, in my opinion, is that data scientists are tasked with making raw data usable while statisticians seem to begin their analysis and modeling with data that is already in a usable format. On the other hand, I think data scientists and statisticians are similar because they both have the goal of pulling meaningful insights out of their data.

### How do you view yourself in relation to these two areas?

When comparing data scientists and statisticians, I view myself more in the category of being a data scientist. Even though it is not everyone's favorite, I enjoying wrangling data to make it usable. It may take up a lot of time, but once it is cleaned, it feels very fulfilling to be able to successfully create summary statistics and visuals.

## Iris and Petal Width (R Code)

We will first create an object, "y", that represents the density of *Petal Width* in the Iris data set.

```{r}
y <- density(iris$Petal.Width)
```

Then, we will determine the class, type, and structure of the object "y".

```{r}
class(y)
typeof(y)
str(y)
```

Now, we will plot the object "y".

```{r}
#| echo: FALSE
plot(y, main = "Density of Petal Width", xlab = "Petal Width")
```





